maxent model avec xvalidation (year-based test training)

### 2019-09-09 src/paper2_maxent_avec_xvalidation.Rmd
updating background points for p2

@@

select month
```{r month of interest -change}
mthna <- "mar"
mthno <- "3"
```

@@

>>>>

need to create 10k background points weighted to nafo zones (as per mj)

use the exising file "../output/bio/background/correct_random_files/background_point_na_removal_nona.csv" which contains centroid location for every in the mcp....

```{r}
allbk <- read.csv("../output/bio/background/correct_random_files/background_point_na_removal_nona.csv", header = TRUE)

now you need to select 10k points, weighted by nafo region...

0A	2.4	240
0B	9.6	960
1B	0.2	20
1C	0.8	80
1D	1.5	150
1E	2	200
1F	3.8	380
2G	6.8	680
2H	7.2	720
2J	8.5	850
3K	8.8	880
3L	7.4	740
3M	0.5	50
3N	2.7	270
3O	3.9	390
3Pn	0.3	30
3Ps	4	400
4R	1.9	190
4S	3.7	370
4T	5.1	510
4Vn	1.1	110
4Vs	4	400
4W	4	400
4X	3.8	380
5Y	1.5	150
5Ze	0.5	50
HudsonStrait	4	400

```{r may 1999}
may19990a <- subset(nafo_zone == "0A")
may19990a <- sample_n(may19990a, 14) 
may19990b <- subset(nafo_zone == "0B")
may19990b <- sample_n(may19990b, 58) 
may19991B <- subset(nafo_zone == "1B")
may19991B <- sample_n(may19991B, 1)
may19991C <- subset(nafo_zone == "1C")
may19991C <- sample_n(may19991C, 5) 
may19991d <- subset(nafo_zone == "1D")
may19991d <- sample_n(may19991d, 9)
may19991E <- subset(nafo_zone == "1E")
may19991E <- sample_n(may19991E, 12)
may19991F <- subset(nafo_zone == "1F")
may19991F <- sample_n(may19991F, 23)
may19992G <- subset(nafo_zone == "2G")
may19992G <- sample_n(may19992G, 40) 
may19992H <- subset(nafo_zone == "2H")
may19992H <- sample_n(may19992H, 43) 
may19992J <- subset(nafo_zone == "2J")
may19992J <- sample_n(may19992J, 50) 
may19993k <- subset(nafo_zone == "3K")
may19993k <- sample_n(may19993k, 52) 
may19993L <- subset(nafo_zone == "3L")
may19993L <- sample_n(may19993L, 44)
may19993M <- subset(nafo_zone == "3M")
may19993M <- sample_n(may19993M, 3)
may19993N <- subset(nafo_zone == "3N")
may19993N <- sample_n(may19993N, 16) 
may19993o <- subset(nafo_zone == "3O")
may19993o <- sample_n(may19993o, 23) 
may19993pn <- subset(nafo_zone == "3Pn")
may19993pn <- sample_n(may19993pn, 2) 
may19993ps <- subset(nafo_zone == "3Ps")
may19993ps <- sample_n(may19993ps, 24) 
may19994r <- subset(nafo_zone == "4R")
may19994r <- sample_n(may19994r, 11) 
may19994s <- subset(nafo_zone == "4S")
may19994s <- sample_n(may19994s, 22) 
may19994t <- subset(nafo_zone == "4T")
may19994t <- sample_n(may19994t, 30) 
may19994vn <- subset(nafo_zone == "4Vn")
may19994vn <- sample_n(may19994vn, 6) 
may19994vs <- subset(nafo_zone == "4Vs")
may19994vs <- sample_n(may19994vs, 24) 
may19994w <- subset(nafo_zone == "4W")
may19994w <- sample_n(may19994w, 24) 
may19994x <- subset(nafo_zone == "4X")
may19994x <- sample_n(may19994x, 23) 
may19995Y <- subset(nafo_zone == "5Y")
may19995Y <- sample_n(may19995Y, 9) 
may19995Ze <- subset(nafo_zone == "5Ze")
may19995Ze <- sample_n(may19995Ze, 3) 
may1999hud <- subset(nafo_zone == "HudsonStrait")
may1999hud <- sample_n(may1999hud, 24) 
may1999 <- rbind(may19990a, may19990b, may19991B, may19991C, may19991d, may19991E, may19991F,  may19992G, may19992H, may19992J, may19993k, may19993L, may19993M, may19993N, may19993o, may19993pn, may19993ps, may19994r, may19994s, may19994t, may19994vn, may19994vs, may19994w, may19994x, may19995Y, may19995Ze, may1999hud)
```

@@

select month
```{r month of interest -change}
mthna <- "jan"
mthno <- "1"
```

@@

just checking for no background points... should be 10k per year...
```{r delete me}
prbackb <- subset(prback, occurrence == 0)
byr <- unique(prbackb$year)
```
